Map{R}educe in {MPI} for Large-scale Graph Algorithms

### 2011-03-10 paper/results.tex
Updated line counts. Finished proofs for submission
git-svn-id: svn+ssh://software-srn.sandia.gov/svn/mapreduce/trunk@866 3fc257bb-8550-0410-81b3-a5c103da83f7

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
\hline
Algorithm & R-MAT & R-MAT++ & PageRank & Tri & CC & MIS & SSSP & SSSP++ \\
\hline
Lines of code & 208 & 216 & 603 & 367 & 453 & 393 & 394 & 448 \\
Figure & \ref{fig:rmat} & \ref{fig:rmat2} & \ref{fig:pr2} & \ref{fig:tri} & \ref{fig:cc} & \ref{fig:luby} & \ref{fig:sssp} & \ref{fig:sssp2} \\
\hline
\end{tabular}
\caption{Lines of code to implement each of the graph
  algorithms in the associated figures.}
\label{t:linecount}
\end{center}
\end{table}

For comparison, we wrote a parallel distributed-memory R-MAT
generation code with explicit MPI calls using a different
(non-MapReduce) algorithm than that of Figures \ref{fig:rmat} and
\ref{fig:rmat2}.  It required 845 lines of code, mainly because it
must implement the parallelism explicitly, whereas the codes of this
section relegate that task to the MR-MPI library.  A similar all-MPI
implementation of the PageRank algorithm required 718 lines.  By
contrast an implementation of PageRank using the Trilinos parallel
linear algebra library (discussed in Section
\ref{subsec:results_pagerank}) required only 153 lines of code, since
entire dot-products and matrix-vector multiplications can be invoked by single function calls to
Trilinos.  Our collaborators (see Acknowledgments) have a Hadoop
implementation of the SSSP algorithm of Figure \ref{fig:sssp}.  It
required 697 lines of Java.

>>>>

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
\hline
Algorithm & R-MAT & R-MAT++ & PageRank & Tri & CC & MIS & SSSP & SSSP++ \\
\hline
Lines of code & 161 & 163 & 463 & 266 & 254 & 291 & 243 & 262 \\
Figure & \ref{fig:rmat} & \ref{fig:rmat2} & \ref{fig:pr2} & \ref{fig:tri} & \ref{fig:cc} & \ref{fig:luby} & \ref{fig:sssp} & \ref{fig:sssp2} \\
\hline
\end{tabular}
\caption{Lines of code to implement each of the graph
  algorithms in the associated figures.}
\label{t:linecount}
\end{center}
\end{table}

For comparison, we wrote a parallel distributed-memory R-MAT
generation code with explicit MPI calls using a different
(non-MapReduce) algorithm than that of Figures \ref{fig:rmat} and
\ref{fig:rmat2}.  It required 453 lines of code, mainly because it
must implement the parallelism explicitly, whereas the codes of this
section relegate that task to the MR-MPI library.  A similar all-MPI
implementation of the PageRank algorithm required 506 lines.  By
contrast an implementation of PageRank using the Trilinos parallel
linear algebra library (discussed in Section
\ref{subsec:results_pagerank}) required only 76 lines of code, since
entire dot-products and matrix-vector multiplications can be invoked by single function calls to
Trilinos.  Our collaborators (see Acknowledgments) have a Hadoop
implementation of the SSSP algorithm of Figure \ref{fig:sssp}.  It
required 527 lines of Java.
